\begin{rubric}{Selected Projects}

\subrubric{Nanofabrication}
\entry* \textbf{Si$_3$N$_4$ nanobeam cavities and grating couplers} --- Designed/fabricated various cavity geometries with optical $Q\sim 10{,}000$ and mode volume $\sim(2.5\,\lambda/n)^3$ and grating couplers with $20\%$ coupling efficiency.\par
% \entry* \textbf{Grating couplers} --- Designed/fabricated couplers for waveguide circuits with $20\%$ coupling efficiency.\par
% \entry* \textbf{Metal microfabrication} --- Photolithography, deposition, and liftoff for simple structures.\par

\subrubric{Optics}
\entry* \textbf{Confocal microscopes} --- Built several scanning confocal microscopes in different configurations (galvos vs. motorized stages and free-space vs. optical fiber spatial filtering). \par
\entry* \textbf{Time-domain quantum emitter measurements} --- Photon correlation Fourier spectroscopy, Hanbury Brown-Twiss measurement, and fluorescence lifetime of individual quantum emitters.\par
% \entry* \textbf{EOM laser chopper} --- Used two cascaded fiber EOMs to achieve laser extinction in $<800$ ps.\par
\entry* \textbf{Lasers \& cavities} --- Aligned several MSquared Ti:sapphire lasers and high-finesse cavities.\par
% \entry* \textbf{Spectrometers/monochromators} --- Built grating-based instruments with motorized rotation stages and camera/fiber readout.\par
% \entry*\textbf{Quantum emitter spectroscopy} --- Developed techniques for measuring transition linewidths, fluorescence lifetime, Hanbury Brown-Twiss and Hong-Ou-Mandel measurements
\entry*\textbf{Extreme cross-polarization extinction} --- Developed precision optics for cross-polarization extinction with visibility $>70$~dB. 

\subrubric{Micromechanics}
\entry* \textbf{Crystal micromanipulator} --- Positioned 30~\textmu m crystals onto nanophotonic devices using a tapered fiber on a 3D micropositioner.\par
\entry* \textbf{Motorized XY stage} --- Built precision stage for heavy loads ($>25$~lbs) with $<2$~\textmu m repeatability.\par
% \entry* \textbf{Fiber tapering apparatus} --- Precision tapering setup using controlled drawing through HF acid.\par

\subrubric{Programming, electronics, and automation}
\entry* \textbf{Experiment automation} --- Python based GUI and custom drivers for remote/automated experiments: FAST Comtec and Swabian time taggers (Python), M Squared laser (TCP/IP), various optomechanical instruments (NI-DAQ, Python), and custom instruments (ARduino, RPi, ESP32). \par
\entry* \textbf{Low-cost photon counter} --- ESP32-based solution for low-time resolution photon counting.\par
\entry* \textbf{Remote lab monitoring} --- RPi/Arduino sensors + Grafana temperature monitoring.\par
% \entry* \textbf{Distributed simulation} --- Python-based distributed computing for Lumerical FDTD.\par

\subrubric{Theory}
\entry* \textbf{Collective quantum systems} --- QuTiP-based simulator for collective interactions.\par
\entry* \textbf{Electromagnetic scattering} --- Analytical and numerical modeling of reflection from periodic metal grids (undergraduate thesis topic).\par
\entry* \textbf{Probability and linear algebra course development} --- Assisted in developing courses for probability and statistics and linear algebra based on Jupyter notebooks. 

\subrubric{Materials synthesis}
\entry* \textbf{DBT:anthracene crystal growth} --- Built a custom two-stage tube furnace for vapor-phase growth of ultra-high aspect-ratio crystals and implemented a protocol for solution-based growth of DBT-doped anthracene nanocrystals.\par

\subrubric{Graphic design}
\entry* {Various scientific graphics made in Blender, Inkscape, and Adobe Illustrator for publications and presentations.}\par

\subrubric{Machining and 3D printing}
\entry* {Basic 3D printing and use of end mills for making custom lab components.}

\end{rubric}
