\begin{rubric}{Posters and Talks}

\subrubric{Oral Presentations}

\entry*[Jan 2026]%
\emph{Cavity QED with individual cryogenic molecules}, SPIE Photonics West\par

\entry*[Apr 2024]%
\emph{Superradiant and subradiant states in lifetime-limited organic molecules}, Second Annual Birck Symposium.\par

\entry*[Apr 2024]%
\emph{Workshop: A visual introduction to quantum optics}, Quantum Science at Purdue.\par

\entry*[Sept 2023]%
\emph{Seminar: Superradiant and subradiant states in lifetime-limited organic molecules through laser-induced tuning}, Purdue AMO-QIS.\par

\entry*[Oct 2022]%
\emph{Organic dye molecules as a platform for coherent light--matter interactions}, Quantum Advances Seminar.\par

\entry*[Apr 2021]%
\emph{Electromagnetic scattering from periodic conducting arrays}, USU Student Research Symposium.\par

\entry*[Dec 2020]%
\emph{Modeling reflectance spectra of nanorod arrays by arrays of light sources}, USU Student Research Symposium.\par

\entry*[Oct 2020]%
\emph{Modeling reflectance spectra of nanorod arrays by arrays of light sources}, APS Four Corners Section.\par

\entry*[Feb 2020]%
\emph{How to create very dark surfaces for applications}, Utah Conference on Undergraduate Research.\par

\entry*[Oct 2019]%
\emph{Synthesis of carbon nanotube forests on deep-etched patterns for light absorption}, APS Four Corners Section.\par

\subrubric{Poster Presentations}

\entry*[Aug 2024]%
\emph{Scalable collective systems through laser-induced frequency tuning of organic molecules}, Cooperative Phenomena in Hybrid Quantum Systems Workshop.\par

\entry*[June 2023]%
\emph{Coupling organic molecules to nanophotonic cavities to study collective effects}, DAMOP.\par

\entry*[Apr 2023]%
\emph{Tailoring the entanglement of quantum emitters through light-induced frequency tuning}, Purdue Quantum Summer School.\par

\entry*[Oct 2021]%
\emph{Scattering of light from periodic conducting structures}, APS Four Corners Section (co-author).\par

\entry*[Apr 2019]%
\emph{Fabrication of carbon-nanotube based bolometers}, USU Student Research Symposium.\par

\end{rubric}
